\thispagestyle{plain}
\section*{Acknowledgements}
First and foremost I would like to thank my supervisor Prof. Jan M. Pawlowski for giving me the opportunity to work on my desired topic and for always finding the time to discuss about open questions and the physical concepts this work is based on. I learned a lot about theoretical physics and had the chance to get in contact with a very interesting, modern research topic.\\
I want to thank Prof. J\"org J\"ackel for his interest and for agreeing to become the second referee for this thesis.\\
Maybe the most important new experience for me was to be part of a research group and I have to say that I had a really great time at Philosophenweg 12! I have to thank the whole Quantum Gravity group for the nice atmosphere and many interesting and helpful discussions. Especially, I have to thank Gustavo Brito for all the time he invested  to answer my questions. The countless blackboard sessions improved my understanding of the subject a lot. I am also thankful for his valuable comments on the presentation of the conducted calculations.\\
For careful proofreading of some parts of this thesis and many ideas on how to improve this work, I have to thank my friends Benjamin Bentner, Niklas Merk and Carl von Randow. I would particularly like to thank my friends Mercal Abdin and Marie Wintergerst for their interest and effort in proofreading the introductory parts of this thesis. \\
Lastly, I thank all my friends for the great time we spent together over the last years, no matter whether in Heidelberg or at home! Of course, I can not thank my parents Marie-Paule and Bernd Kaltschmidt and my sister C\'{e}line enough for their constant support and for always helping me to pursue my dreams.  
 
\vfill
\section*{Declaration of Authorship}
I hereby certify that this thesis has been composed by me and is based on my own work, unless stated otherwise.\\

Heidelberg, 8$^{\mathrm{th}}$ of July 2019 \hfill \rule{60mm}{.15mm} \par \vspace{-0.4cm}
\hfill Mathieu Kaltschmidt
\vfill

